Estimating associations between childhood exposure to non-persistent endocrine disruptors, corticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2023-12-28 output/paper/manuscript.qmd
Working on manuscript.

Our results are consistent with prior research that associated exposure to certain \acr{edcs} with higher levels of urinary cortisol [@KimLeeMoon:2018; @SearsLiuLanphear:2023]. Contrary to these prior studies, we did find effect modification by sex. We are not aware of other epidemiological studies investigating phthalates metabolites, phenols, and \acr{opps}, in relation to urinary glucocorticoids in childhood.
We are also not aware of prior studies specifically investigating the effects of exposure to \acr{edcs} and elevated levels of glucocorticoids in relation to \acr{hitrtse}.

>>>>

Our results are consistent with prior research that associated exposure to certain \acr{edcs} with higher levels of urinary and hair cortisol [@KimLeeMoon:2018; @SearsLiuLanphear:2023]. Contrary to these prior studies, we did find effect modification by sex. We are not aware of other epidemiological studies investigating phthalates metabolites, phenols, and \acr{opps}, in relation to urinary glucocorticoids in childhood.
We are also not aware of prior studies specifically investigating the effects of exposure to \acr{edcs} and elevated levels of glucocorticoids in relation to \acr{hitrtse}.
